Blocking-resistant communication\\through domain fronting

### 2014-08-01 docs/meek.tex
Blind references to Lantern and Psiphon.

We have implemented domain fronting in a system called \meek,
a pluggable transport for Tor.
\meek\ combines fronting with a proxy server that encodes a TCP stream
as a sequence of HTTP requests and responses.
The \meek\ server's external interface is that of an ordinary web server.
Domain fronting enables a client to reach the server.
The server receives requests, decodes them, and feeds their payloads into a Tor relay,
and returns downstream data in the HTTP response.
A censor watching the communication sees only a sequence of HTTPS requests to an allowed domain.
We describe the results of an initial deployment.
\meek, or something based on it,
has been adopted by other circumvention systems including Lantern and Psiphon.

@@

\meek\ has been built into an alpha version of Tor Browser,
and has a small number of users.
Our deployment so far uses Google App Engine and Amazon CloudFront.
% with the hidden actual domain \urll{meek-reflect.appspot.com}
% hidden by the front \urll{www.google.com}.
Section~\ref{sec:deployment} discusses other fronting-capable services
and deployment scenarios.
In addition to the Tor pluggable transport,
systems based on \meek\ are now used by other circumvention systems
including Psiphon~\cite{psiphon} and Lantern~\cite{lantern}.

@@

Psiphon~\cite{psiphon} is a network of many one-hop proxies,
with encryption and traffic obfuscation between client and server.
Psiphon uses domain fronting based on \meek\ as one of its blocking defenses since June~2014~\cite{psiphon-meek-merge}.
Lantern~\cite{lantern} uses a network of proxies running on volunteer computers;
proxy addresses are shared only with trusted friends in order to make them difficult to enumerate.
Lantern~1.4 is planned to use domain fronting inspired by \meek~\cite{lantern-1.3.1}.

@@

HTTP is fundamentally a request-based protocol.
There is no way for the server to ``push'' data to the client without
having first received a request.
In order to enable the server to send back data,
\meek\ uses one of two techniques.
The first is polling:
every so often the client sends a request with an empty payload
if it has nothing else to send,
simply to give the server an opportunity to reply.
The polling interval starts short (100~ms) and grows exponentially
up to a maximum of 5~s.
The other technique,
implemented in Psiphon's version of \meek,
uses long-lived persistent HTTP connections.
When the server sends a response, it keeps the connection open,
continually appending data to the response body while it has anything to send.
When the server receives a new request from the same client,
it closes any response stream it has open to the client and starts a new one.
This second technique is especially beneficial for bulk downloads,
but doesn't work on all services:
notably Google App Engine doesn't support streaming of this kind.

@@

% >>> (1*543+450.)/(1*543)
% 1.828729281767956
% >>> (2*543+450.)/(2*543)
% 1.4143646408839778
% >>> (3*543+450.)/(3*543)
% 1.276243093922652
\noindent
The total overhead varies according to the length
of the Host field and the specifics of the intermediate web service's TLS,
but is somewhere in the neighborhood of $(543+450)/543-1\approx83$\%.
This is the worst case, when Tor sends a single cell.
Tor can bunch multiple cells into one transmission;
if two cells are sent at once, the overhead drops to
${\approx}41$\%; if three, it is ${\approx}28$\%.
Bulk uploads and downloads tend to have less overhead, bunching many cells at once.
Persistent HTTP connections as used by Psiphon reduce overhead further,
because only one HTTP header is needed for a large number of transmissions.
Empty polling requests also use bandwidth,
but they are sent only when the connection is idle
so they don't affect upload or download speed.
As is discussed in Section~\ref{sec:trafficanalysis},
\meekclient reuses the same TLS connection for many requests,
so the fixed overhead of the initial TLS handshake is amortized.

@@

There is additional latency overhead caused by meek's extra network hop:
rather than accessing the Tor bridge directly,
the client first goes to the intermediate web service.
How much latency the extra hop adds depends, of course, on the network location
of the client, web service, and Tor bridge.
Strict serialization of requests and responses
becomes a problem with large round-trip times,
as throughput becomes limited by latency.
Section~\ref{sec:discussion} describes ways to improve
performance with high latencies;
Psiphon's use of persistent connections as described in this section is one of them.

@@

Appropriate TLS camouflage may differ depending on circumstances.
On a traditional desktop PC, using a browser is probably the right choice.
When Psiphon ported \meekclient to Android,
they didn't use a browser as camouflage,
but rather made all HTTPS requests with the standard Android HTTP API.
This decision makes sense because other Android applications
also use the standard API and share the same TLS fingerprint.

@@

Development on \meek\ as a Tor pluggable transport~\cite{pt} began in January~2014.
Most users who use Tor, use it with Tor Browser~\cite{torbrowser},
a customized version of Firefox that is
preconfigured to use a built-in Tor client.
% and patched to defend against application-layer privacy and anonymity threats
% like tracking cookies and web browser fingerprinting.
Tor Browser has an easy interface for selecting pluggable transports.
We made a series experimental releases of Tor Browser featuring \meek,
releasing the first one on February~18.
On April~18 we made the first release featuring the browser camouflage
that is the subject of Section~\ref{sec:browserextension}.
We announced our releases on Tor development mailing lists,
whence they were picked up by Tor Weekly News on the Tor blog.
Our code was merged by the Tor Browser maintainers
in June and is scheduled for an alpha release,
still pending as of this writing.

@@

\begin{figure}
\includegraphics[width=\linewidth]{clients-psiphon3}
\caption{
Daily unique users of \meek\ with Psiphon (note vertical axis).
The decrease at the end of June
was caused by an unblocking event that made \meek\ unnecessary for some users.
}
\label{fig:clients-psiphon3}
\end{figure}

@@

Psiphon began their deployment of \meek\ in June~2014.
Figure~\ref{fig:clients-psiphon3} shows the number
of unique daily users of \meek\ with Psiphon,
estimated through clients' self-reporting of their most recent connection date.
The Psiphon developers tell us that the drop that occurs
in the middle of June was not caused by a blocking event,
but rather an unblocking event that made \meek\ unnecessary for some users.
Although Figures~\ref{fig:clients-tor} and~\ref{fig:clients-psiphon3}
are not directly comparable because they count slightly different things,
it is clear that meek-with-Psiphon, with its thousands of daily users,
is much more widely used than meek-with-Tor, which has not yet seen a formal release,

@@

We have presented domain fronting,
an HTTPS technique that uses different domain names
at different communication layers in
order to hide the remote endpoint of a communication.
We implemented \meek,
a pluggable transport for Tor.
We show that it resists common methods of blocking,
and begin an investigation into its
resistance against more subtle and expensive means of traffic analysis.
We discuss the results of an initial deployment of \meek\
in both Tor and Psiphon.

>>>>

We have implemented domain fronting in a system called \meek,
a pluggable transport for Tor.
\meek\ combines fronting with a proxy server that encodes a TCP stream
as a sequence of HTTP requests and responses.
The \meek\ server's external interface is that of an ordinary web server.
Domain fronting enables a client to reach the server.
The server receives requests, decodes them, and feeds their payloads into a Tor relay,
and returns downstream data in the HTTP response.
A censor watching the communication sees only a sequence of HTTPS requests to an allowed domain.
We describe the results of an initial deployment.
\meek, or something based on it,
has been adopted by other circumvention systems including
[blinded for anonymous submission].
% ANON
% Lantern and Psiphon.

@@

\meek\ has been built into an alpha version of Tor Browser,
and has a small number of users.
Our deployment so far uses Google App Engine and Amazon CloudFront.
% with the hidden actual domain \urll{meek-reflect.appspot.com}
% hidden by the front \urll{www.google.com}.
Section~\ref{sec:deployment} discusses other fronting-capable services
and deployment scenarios.
In addition to the Tor pluggable transport,
systems based on \meek\ are now used by other circumvention systems including
[blinded for anonymous submission].
% ANON
% including Psiphon~\cite{psiphon} and Lantern~\cite{lantern}.

@@

Psiphon~\cite{psiphon} is a network of many one-hop proxies,
with encryption and traffic obfuscation between client and server.
% ANON
% Psiphon uses domain fronting based on \meek\ as one of its blocking defenses since June~2014~\cite{psiphon-meek-merge}.
Lantern~\cite{lantern} uses a network of proxies running on volunteer computers;
proxy addresses are shared only with trusted friends in order to make them difficult to enumerate.
% ANON
% Lantern~1.4 is planned to use domain fronting inspired by \meek~\cite{lantern-1.3.1}.

@@

HTTP is fundamentally a request-based protocol.
There is no way for the server to ``push'' data to the client without
having first received a request.
In order to enable the server to send back data,
\meek\ uses one of two techniques.
The first is polling:
every so often the client sends a request with an empty payload
if it has nothing else to send,
simply to give the server an opportunity to reply.
The polling interval starts short (100~ms) and grows exponentially
up to a maximum of 5~s.
% ANON
% The other technique,
% implemented in Psiphon's version of \meek,
The other technique
uses long-lived persistent HTTP connections.
When the server sends a response, it keeps the connection open,
continually appending data to the response body while it has anything to send.
When the server receives a new request from the same client,
it closes any response stream it has open to the client and starts a new one.
This second technique is especially beneficial for bulk downloads,
but doesn't work on all services:
notably Google App Engine doesn't support streaming of this kind.

@@

% >>> (1*543+450.)/(1*543)
% 1.828729281767956
% >>> (2*543+450.)/(2*543)
% 1.4143646408839778
% >>> (3*543+450.)/(3*543)
% 1.276243093922652
\noindent
The total overhead varies according to the length
of the Host field and the specifics of the intermediate web service's TLS,
but is somewhere in the neighborhood of $(543+450)/543-1\approx83$\%.
This is the worst case, when Tor sends a single cell.
Tor can bunch multiple cells into one transmission;
if two cells are sent at once, the overhead drops to
${\approx}41$\%; if three, it is ${\approx}28$\%.
Bulk uploads and downloads tend to have less overhead, bunching many cells at once.
Persistent HTTP connections, when they are possible, reduce overhead further,
% ANON
% Persistent HTTP connections as used by Psiphon reduce overhead further,
because only one HTTP header is needed for a large number of transmissions.
Empty polling requests also use bandwidth,
but they are sent only when the connection is idle
so they don't affect upload or download speed.
As is discussed in Section~\ref{sec:trafficanalysis},
\meekclient reuses the same TLS connection for many requests,
so the fixed overhead of the initial TLS handshake is amortized.

@@

There is additional latency overhead caused by meek's extra network hop:
rather than accessing the Tor bridge directly,
the client first goes to the intermediate web service.
How much latency the extra hop adds depends, of course, on the network location
of the client, web service, and Tor bridge.
Strict serialization of requests and responses
becomes a problem with large round-trip times,
as throughput becomes limited by latency.
Section~\ref{sec:discussion} describes ways to improve
% ANON
% performance with high latencies;
% Psiphon's use of persistent connections as described in this section is one of them.

@@

Appropriate TLS camouflage may differ depending on circumstances.
On a traditional desktop PC, using a browser is probably the right choice.
When
[blinded circumcention tool]
% ANON
% Psiphon
ported \meekclient to Android,
they didn't use a browser as camouflage,
but rather made all HTTPS requests with the standard Android HTTP API.
This decision makes sense because other Android applications
also use the standard API and share the same TLS fingerprint.

@@

Development on \meek\ as a Tor pluggable transport~\cite{pt} began in January~2014.
Most users who use Tor, use it with Tor Browser~\cite{torbrowser},
a customized version of Firefox that is
preconfigured to use a built-in Tor client.
% and patched to defend against application-layer privacy and anonymity threats
% like tracking cookies and web browser fingerprinting.
Tor Browser has an easy interface for selecting pluggable transports.
We made a series experimental releases of Tor Browser featuring \meek,
releasing the first one on February~18.
[Some details of deployment are omitted for anonymous submission.]
% ANON
% On April~18 we made the first release featuring the browser camouflage
% that is the subject of Section~\ref{sec:browserextension}.
% We announced our releases on Tor development mailing lists,
% whence they were picked up by Tor Weekly News on the Tor blog.
% Our code was merged by the Tor Browser maintainers
% in June and is scheduled for an alpha release,
% still pending as of this writing.

@@

\begin{figure}
\includegraphics[width=\linewidth]{clients-psiphon3}
\caption{
Daily unique users of \meek\ with
[blinded circumvention tool]
% ANON
% Psiphon
(note vertical axis).
The decrease at the end of June
was caused by an unblocking event that made \meek\ unnecessary for some users.
}
\label{fig:clients-psiphon3}
\end{figure}

@@

[Blinded circumvention tool]
% ANON
% Psiphon
began their deployment of \meek\ in June~2014.
Figure~\ref{fig:clients-psiphon3} shows the number
of unique daily users of \meek%
,
% ANON
% with Psiphon,
estimated through clients' self-reporting of their most recent connection date.
The developers tell us that the drop that occurs
in the middle of June was not caused by a blocking event,
but rather an unblocking event that made \meek\ unnecessary for some users.
Although Figures~\ref{fig:clients-tor} and~\ref{fig:clients-psiphon3}
are not directly comparable because they count slightly different things,
it is clear that meek-with-%
[blinded circumvention tool],
% ANON
% Psiphon,
with its thousands of daily users,
is much more widely used than meek-with-Tor, which has not yet seen a formal release,

@@

We have presented domain fronting,
an HTTPS technique that uses different domain names
at different communication layers in
order to hide the remote endpoint of a communication.
We implemented \meek,
a pluggable transport for Tor.
We show that it resists common methods of blocking,
and begin an investigation into its
resistance against more subtle and expensive means of traffic analysis.
We discuss the results of an initial deployment.
% ANON
% in both Tor and Psiphon.
